---
title: "Report template"
author: Meg Oshima and Nicholas Ducharme-Barth with JB
format:
  html:
    embed-resources: true
params:
  parameter: "steepness"
  model1_dir: "steepness-0.5"
  model2_dir: "steepness-0.7"
---

```{r}
#| message: false
library(r4ss)
library(dplyr)
library(stringr)
library(magrittr)
library(ggplot2)

main_dir <- this.path::this.proj()

report1 <- SS_output(dir = file.path(main_dir, "stock-synthesis-models", params$model1_dir), verbose=FALSE, printstats=FALSE)
new_steep1 <- report1$parameters %>% 
             filter(str_detect(Label, "SR_BH_steep")) %>% ## Need to change this to match the parameter name in control file
             pull(Value)

report2 <- SS_output(dir = file.path(main_dir, "stock-synthesis-models", params$model2_dir), verbose=FALSE, printstats=FALSE)
new_steep2 <- report2$parameters %>% 
             filter(str_detect(Label, "SR_BH_steep")) %>% ## Need to change this to match the parameter name in control file
             pull(Value)
```

# Model modifications description

I changed the `r params$parameter` to `r new_steep1` and `r new_steep2`.

# Plot of SSB for Steepness = `r new_steep1`

Here is a plot showing the timeseries of SSB for the modified model with `r params$parameter`=`r new_steep1`.

```{r}
#| code-fold: true
ssb_summary <- report1$timeseries %>% 
               select(Yr, SpawnBio) %>%
               mutate(model_name = params$model1_dir)

ssb_summary %>%
    ggplot() +
    geom_line(aes(x = Yr, y = SpawnBio)) + 
    xlab("Year") + 
    ylab("Spawning Biomass") +
    theme(panel.background = element_rect(fill = "white", color = "black", linetype = "solid"),
                panel.grid.major = element_line(color = 'gray70',linetype = "dotted"), 
                panel.grid.minor = element_line(color = 'gray70',linetype = "dotted"),
                strip.background =element_rect(fill="white"),
                legend.key = element_rect(fill = "white"))
```

# Plot of SSB for Steepness = `r new_steep2`

Here is a plot showing the timeseries of SSB for the modified model with `r params$parameter`=`r new_steep2`.

```{r}
#| code-fold: true
ssb_summary <- report2$timeseries %>% 
               select(Yr, SpawnBio) %>%
               mutate(model_name = params$model2_dir)

ssb_summary %>%
    ggplot() +
    geom_line(aes(x = Yr, y = SpawnBio)) + 
    xlab("Year") + 
    ylab("Spawning Biomass") +
    theme(panel.background = element_rect(fill = "white", color = "black", linetype = "solid"),
                panel.grid.major = element_line(color = 'gray70',linetype = "dotted"), 
                panel.grid.minor = element_line(color = 'gray70',linetype = "dotted"),
                strip.background =element_rect(fill="white"),
                legend.key = element_rect(fill = "white"))
```
